# blinded B64

```{r ,include=FALSE}
library(Rose)
library(ggplot2)
library(plotly)
library(knitr)
# library(hadron)
#library(kableExtra) # breaks latex
#library(tidyverse)

df <- data.frame(x = 1:5, y = 1:5)
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knit handle the plot
myplotly(ggplot())
#widgetframe::frameableWidget(ggplotly(ggp)%>%config(mathjax = "cdn") )
```
the different bounding are:

- Above
  
  1) $c(t>t_c)< c(t_c) e^{-E_{2\pi} (t-t_c)}$
  
  2) $c(t>t_c)< c(t_c) e^{-M_{eff} (t-t_c)}$
    where $M_{eff}$ is the plateau value of $m_{eff}(t)$ of the correlator VKVK.

- below 

  1) $c(t>t_c) > 0$
  
  2) $c(t>t_c)< c(t_c) e^{-m_{eff}(t_m) (t-t_c)}$, where $t_m=t_c$ for  $t_c<t_e$
    while $t_m=t_e$ for $t_c\geq t_e$ and $t_e$ is some time slice

The different labels refer to:

- amu_{bound}_(TM)_below: bounding above 1. and below 1. (BMW)

- amu_{bound_meff_t}_(TM)_below: bounding above 1. and below 2. (ROME)

- amu_{bound_meff}_(TM)_below:  bounding above 2. and below 2. 



```{r, results='asis',echo=FALSE}
source("/home/garofalo/programs/Rose/R/plot_routines.R")
e<-"B64"
dir <-"/home/garofalo/analysis/blinded_gm2/data/out/"
df<-NULL
mt<-read_df(paste0(dir,e,"_output"))
all_obs<-Rose::get_all_corr(mt)
df<-add_corr_to_df("amu_{bound}_(TM)_above",all_obs ,mt,df, 
                   reshape = FALSE, print_res = FALSE, ifit=5, idfit=6
                   )
df<-add_corr_to_df("amu_{bound}_(TM)_below",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.2, ifit=5, idfit=6
                   )
df<-add_corr_to_df("amu_{bound_meff_t}_(TM)_below",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.1, ifit=5, idfit=6
                   )
df<-add_corr_to_df("amu_{bound_meff}_(TM)_above",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.3, ifit=5, idfit=6
                   )

df1<- get_block("amu_{full}_(TM)",all_obs ,mt,NULL ,log=FALSE,number=NULL,
                     nudge=0.0, print_res=FALSE , rename="integrand", 
                     logx=0, ix=1, iy=7, ierr=8, ifit=5, ierrfit=6, iplateau=1)

# df2<- get_block("amu_{full}_(TM)",all_obs ,mt,NULL ,log=FALSE,number=NULL,
#                      nudge=0.0, print_res=FALSE , rename="corr", 
#                      logx=0, ix=1, iy=9, ierr=10, ifit=5, ierrfit=6, iplateau=1)
# # df2$y<-df1$y/df2$y  ## to get the kernel K

gg<-plot_df_corr_ggplot(df)
gg<-plot_df_corr_ggplot(df1,gg=gg,noribbon = TRUE)
# gg<-plot_df_corr_ggplot(df2,gg=gg,noribbon = TRUE)

fig<-myplotly(gg, to_print = TRUE)
```




```{r, results='asis',echo=FALSE}
e<-"B64"
dir <-"/home/garofalo/analysis/blinded_gm2/data/out/"
df<-NULL
mt<-read_df(paste0(dir,e,"_output"))
all_obs<-Rose::get_all_corr(mt)
df<-add_corr_to_df("amu_{bound}_(OS)_above",all_obs ,mt,df, 
                   reshape = FALSE, print_res = FALSE, ifit=5, idfit=6
                   )
df<-add_corr_to_df("amu_{bound}_(OS)_below",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.2, ifit=5, idfit=6
                   )
#   
df<-add_corr_to_df("amu_{bound_meff_t}_(OS)_below",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.1, ifit=5, idfit=6
                   )
df1<- get_block("amu_{full}_(OS)",all_obs ,mt,NULL ,log=FALSE,number=NULL,
                     nudge=0.0, print_res=FALSE , rename="integrand", 
                     logx=0, ix=1, iy=7, ierr=8, ifit=5, ierrfit=6, iplateau=1)
df<-add_corr_to_df("amu_{bound_meff}_(OS)_above",all_obs ,mt,df,
                  reshape = FALSE, nudge = 0.3, ifit=5, idfit=6
                  )

# df<-add_corr_to_df("amu_{bound_meff}_(OS)_below",all_obs ,mt,df,
#                    reshape = FALSE, nudge = 0.1
#                    )

gg<-plot_df_corr_ggplot(df)
gg<-plot_df_corr_ggplot(df1,gg=gg,noribbon = TRUE)

fig<-myplotly(gg, to_print = TRUE)
```

## effective mass VKVK

vertical line at $t_e$ which correspond to the last mass used in the bounding of 
$a_\mu$, i.e. for $t_{cut}> t_e$ we use $m_{eff}(t_{e})$

```{r, results='asis',echo=FALSE}
source("/home/garofalo/programs/Rose/R/plot_routines.R")

e<-"B64"
dir <-"/home/garofalo/analysis/blinded_gm2/data/out/"
df<-NULL
mt<-read_df(paste0(dir,e,"_output"))
all_obs<-Rose::get_all_corr(mt)
df<-add_corr_to_df("M_VKVK_TM",all_obs ,mt,df, 
                   reshape = TRUE
                   )
df<-add_corr_to_df("M_VKVK_OS",all_obs ,mt,df,
                   reshape = TRUE, nudge = 0.1
                   )

gg<-plot_df_corr_ggplot(df, extra_length_plateau = 0.4) 
fit<-get_full_res("amu_{bound_meff_t}_(TM)_below",all_obs ,mt )
gg<- gg + geom_vline(xintercept = fit[1,3], color="black")

fit<-get_full_res("amu_{bound_meff_t}_(OS)_below",all_obs ,mt )
gg<- gg + geom_vline(xintercept = fit[1,3]+0.3, color="blue")
# gg<- gg+ geom_abline(intercept = 37, slope = -5, color="M_VKVK_OS", 
#                  linetype="dashed", size=1.5)
aMpi <- get_full_res("aMpi", all_obs, mt)
a_fm <- get_full_res("a_fm", all_obs, mt)
L_a <- get_full_res("L_a", all_obs, mt)
hbc<- 197.326963
E2<- 2*sqrt( aMpi[1,1]^2 + (2*pi/L_a[1,1])^2 )
gg<- gg+ geom_line(aes(x=c(1:L_a[1,1]), y=rep(E2,L_a[1,1]), color="$\\pi\\pi$"  )  )
Erho<- 700*a_fm[1,1]/hbc
gg<- gg+ geom_line(aes(x=c(1:L_a[1,1]), y=rep(Erho,L_a[1,1]), color="700Mev"  )  )

fig<-myplotly(gg, to_print = TRUE)
```


## FVE

```{r, results='asis',echo=FALSE}
source("/home/garofalo/programs/Rose/R/read_block.R")
e<-"B64"
dir <-"/home/garofalo/analysis/blinded_gm2/data/out/"
mt<-read_df(paste0(dir,e,"_output"))
all_obs<-Rose::get_all_corr(mt)
fit<-get_full_res("DV_DM",all_obs ,mt)
cat("DV_DM = ",fit[1,1]," +- ", fit[1,2],"\n\n")
fit<-get_full_res("DV_to_C80",all_obs ,mt)
cat("DV_to_C80 = ",fit[1,1]," +- ", fit[1,2],"\n\n")
```


## rew


```{r, results='asis',echo=FALSE}
source("/home/garofalo/programs/Rose/R/plot_routines.R")
e<-"B64"
file <-"/home/garofalo/analysis/blinded_gm2/data_tov/out/B64_reweight_strange_OS_B64_LMA.dat_output"
df<-NULL
mt<-read_df(file)
all_obs<-Rose::get_all_corr(mt)
df<-add_corr_to_df("VKVK_TM",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.1, ifit=4, idfit=5, log = TRUE
                   )
df<-add_corr_to_df("VKVK_OS",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.3, ifit=4, idfit=5, log = TRUE
                   )

df<-add_corr_to_df("VKVK_TM_rew",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.1, ifit=4, idfit=5, log = TRUE
                   )
df<-add_corr_to_df("VKVK_OS_rew",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.3, ifit=4, idfit=5, log = TRUE
                   )



gg<-plot_df_corr_ggplot(df)
# gg<-plot_df_corr_ggplot(df2,gg=gg,noribbon = TRUE)

fig<-myplotly(gg, to_print = TRUE)
```


```{r, results='asis',echo=FALSE}
source("/home/garofalo/programs/Rose/R/plot_routines.R")
e<-"B64"
file <-"/home/garofalo/analysis/blinded_gm2/data_tov/out/B64_reweight_strange_OS_B64_LMA.dat_output"
df<-NULL
df1<-NULL
mt<-read_df(file)
all_obs<-Rose::get_all_corr(mt)
df<-add_corr_to_df("amu_{bound_meff_t}_(TM)_below",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.1, ifit=5, idfit=6
                   )
df<-add_corr_to_df("amu_{bound_meff_t}_(TM)_above",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.3, ifit=5, idfit=6
                   )

df<-add_corr_to_df("amu_{bound_meff_t}_(TM)_rew_below",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.1, ifit=5, idfit=6
                   )
df<-add_corr_to_df("amu_{bound_meff_t}_(TM)_rew_above",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.3, ifit=5, idfit=6
                   )

df<-add_corr_to_df("amu_{bound_meff_t}_(OS)_below",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.1, ifit=5, idfit=6
                   )
df<-add_corr_to_df("amu_{bound_meff_t}_(OS)_above",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.3, ifit=5, idfit=6
                   )

df<-add_corr_to_df("amu_{bound_meff_t}_(OS)_rew_below",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.1, ifit=5, idfit=6
                   )
df<-add_corr_to_df("amu_{bound_meff_t}_(OS)_rew_above",all_obs ,mt,df,
                   reshape = FALSE, nudge = 0.3, ifit=5, idfit=6
                   )

df1<- get_block("amu_{full}_(TM)",all_obs ,mt,NULL ,log=FALSE,number=NULL,
                     nudge=0.0, print_res=FALSE , rename="integrand-TM", 
                     logx=0, ix=1, iy=7, ierr=8, ifit=5, ierrfit=6, iplateau=1)
df1<- get_block("amu_{full}_(TM)_rew",all_obs ,mt,df=df1 ,log=FALSE,number=NULL,
                     nudge=0.0, print_res=FALSE , rename="integrand-TM_rew", 
                     logx=0, ix=1, iy=7, ierr=8, ifit=5, ierrfit=6, iplateau=1)


gg<-plot_df_corr_ggplot(df)
gg<-plot_df_corr_ggplot(df1,gg=gg,noribbon = TRUE)
# gg<-plot_df_corr_ggplot(df2,gg=gg,noribbon = TRUE)

fig<-myplotly(gg, to_print = TRUE)
```