# blinded D96

```{r ,include=FALSE}
library(Rose)
library(ggplot2)
library(plotly)
library(knitr)
# library(hadron)
# library(kableExtra) # breaks latex
# library(tidyverse)

df <- data.frame(x = 1:5, y = 1:5)
f1 <- function(df) {
  gg <- ggplot(df, aes(x, y)) +
    geom_point()
  assign("ggp", plotly::ggplotly(gg), envir = parent.frame())
  # ggp
  df # NOT returning a plot
}
res1 <- f1(df)
ggp # Let knit handle the plot
myplotly(ggplot())
# widgetframe::frameableWidget(ggplotly(ggp)%>%config(mathjax = "cdn") )
```
the different bounding are:

- Above
  
  1) $c(t>t_c)< c(t_c) e^{-E_{2\pi} (t-t_c)}$
  
  2) $c(t>t_c)< c(t_c) e^{-M_{eff} (t-t_c)}$
    where $M_{eff}$ is the plateau value of $m_{eff}(t)$ of the correlator VKVK.

- below 

  1) $c(t>t_c) > 0$
  
  2) $c(t>t_c)< c(t_c) e^{-m_{eff}(t_m) (t-t_c)}$, where $t_m=t_c$ for  $t_c<t_e$
    while $t_m=t_e$ for $t_c\geq t_e$ and $t_e$ is some time slice

The different labels refer to:

- amu_{bound}_(TM)_below: bounding above 1. and below 1. (BMW)

- amu_{bound_meff_t}_(TM)_below: bounding above 1. and below 2. (ROME)

- amu_{bound_meff}_(TM)_below:  bounding above 2. and below 2. 



```{r, results='asis',echo=FALSE}
e <- "D96"
dir <- "/home/garofalo/analysis/blinded_gm2/data/out/"
df <- NULL
mt <- read_df(paste0(dir, e, "_output"))
all_obs <- Rose::get_all_corr(mt)
df <- add_corr_to_df("amu_{bound}_(TM)_above", all_obs, mt, df,
  reshape = FALSE, print_res = FALSE, ifit=5, idfit=6
)
df <- add_corr_to_df("amu_{bound}_(TM)_below", all_obs, mt, df,
  reshape = FALSE, nudge = 0.2, ifit=5, idfit=6
)
df <- add_corr_to_df("amu_{bound_meff_t}_(TM)_below", all_obs, mt, df,
  reshape = FALSE, nudge = 0.1, ifit=5, idfit=6
)
df <- add_corr_to_df("amu_{bound_meff}_(TM)_above", all_obs, mt, df,
  reshape = FALSE, nudge = 0.3, ifit=5, idfit=6
)

df1 <- get_block("amu_{full}_(TM)", all_obs, mt, NULL,
  log = FALSE, number = NULL,
  nudge = 0.0, print_res = FALSE, rename = "integrand",
  logx = 0, ix = 1, iy = 7, ierr = 8, ifit = 5, ierrfit = 6, iplateau = 1
)
# df1 <- get_block("amu_{full}_(TM)", all_obs, mt, df1,
#   log = FALSE, number = NULL,
#   nudge = 0.0, print_res = FALSE, rename = "K",
#   logx = 0, ix = 1, iy = 11, ierr = 12, ifit = 5, ierrfit = 6, iplateau = 1
# )
# df2<-df1
# eps<-0.8
# df2$y <- (sin(eps *df1$y ) +sin(eps *df1$y ))/(2*eps)
# df2$label<- "sin"
gg <- plot_df_corr_ggplot(df)
gg <- plot_df_corr_ggplot(df1, gg = gg, noribbon = TRUE)
# gg <- plot_df_corr_ggplot(df2, gg = gg, noribbon = TRUE)

fig <- myplotly(gg, to_print = TRUE)
```




```{r, results='asis',echo=FALSE}
e <- "D96"
dir <- "/home/garofalo/analysis/blinded_gm2/data/out/"
df <- NULL
mt <- read_df(paste0(dir, e, "_output"))
all_obs <- Rose::get_all_corr(mt)
df <- add_corr_to_df("amu_{bound}_(OS)_above", all_obs, mt, df,
  reshape = FALSE, print_res = FALSE, ifit=5, idfit=6
)
df <- add_corr_to_df("amu_{bound}_(OS)_below", all_obs, mt, df,
  reshape = FALSE, nudge = 0.2, ifit=5, idfit=6
)
#
df <- add_corr_to_df("amu_{bound_meff_t}_(OS)_below", all_obs, mt, df,
  reshape = FALSE, nudge = 0.1, ifit=5, idfit=6
)
df1 <- get_block("amu_{full}_(OS)", all_obs, mt, NULL,
  log = FALSE, number = NULL,
  nudge = 0.0, print_res = FALSE, rename = "integrand",
  logx = 0, ix = 1, iy = 7, ierr = 8, ifit = 5, ierrfit = 6, iplateau = 1
)
df <- add_corr_to_df("amu_{bound_meff}_(OS)_above", all_obs, mt, df,
  reshape = FALSE, nudge = 0.3, ifit=5, idfit=6
)

# df<-add_corr_to_df("amu_{bound_meff}_(OS)_below",all_obs ,mt,df,
#                    reshape = FALSE, nudge = 0.1
#                    )

gg <- plot_df_corr_ggplot(df)
gg <- plot_df_corr_ggplot(df1, gg = gg, noribbon = TRUE)

fig <- myplotly(gg, to_print = TRUE)
```

## effective mass VKVK

vertical line at $t_e$ which correspond to the last mass used in the bounding of 
$a_\mu$, i.e. for $t_{cut}> t_e$ we use $m_{eff}(t_{e})$

```{r, results='asis',echo=FALSE}
e <- "D96"
dir <- "/home/garofalo/analysis/blinded_gm2/data/out/"
df <- NULL
mt <- read_df(paste0(dir, e, "_output"))
all_obs <- Rose::get_all_corr(mt)
df <- add_corr_to_df("M_VKVK_TM", all_obs, mt, df,
  reshape = TRUE, ifit=5, idfit=6
)
df <- add_corr_to_df("M_VKVK_OS", all_obs, mt, df,
  reshape = TRUE, nudge = 0.1, ifit=5, idfit=6
)
gg <- plot_df_corr_ggplot(df)
fit <- get_full_res("amu_{bound_meff_t}_(TM)_below", all_obs, mt)
gg <- gg + geom_vline(xintercept = fit[1, 3], color = "black")

fit <- get_full_res("amu_{bound_meff_t}_(OS)_below", all_obs, mt)
gg <- gg + geom_vline(xintercept = fit[1, 3], color = "blue")

aMpi <- get_full_res("aMpi", all_obs, mt)
a_fm <- get_full_res("a_fm", all_obs, mt)
L_a <- get_full_res("L_a", all_obs, mt)
hbc<- 197.326963
E2<- 2*sqrt( aMpi[1,1]^2 + (2*pi/L_a[1,1])^2 )
gg<- gg+ geom_line(aes(x=c(1:L_a[1,1]), y=rep(E2,L_a[1,1]), color="$\\pi\\pi$"  )  )
Erho<- 700*a_fm[1,1]/hbc
gg<- gg+ geom_line(aes(x=c(1:L_a[1,1]), y=rep(Erho,L_a[1,1]), color="700Mev"  )  )


fig <- myplotly(gg, to_print = TRUE)
```

## FVE

```{r, results='asis',echo=FALSE}
source("/home/garofalo/programs/Rose/R/read_block.R")
e <- "D96"
dir <- "/home/garofalo/analysis/blinded_gm2/data/out/"
mt <- read_df(paste0(dir, e, "_output"))
all_obs <- Rose::get_all_corr(mt)
fit <- get_full_res("DV_DM", all_obs, mt)
cat("DV_DM = ", fit[1, 1], " +- ", fit[1, 2], "\n\n")
fit <- get_full_res("DV_to_C80", all_obs, mt)
cat("DV_to_C80 = ", fit[1, 1], " +- ", fit[1, 2], "\n\n")
```

## Statistic


```{r, results='asis',echo=FALSE}

e <- c("D96_444confs", "D96_256confs", "D96_184confs", "D96_122confs")
confs <- c(444,256, 184, 122)

dir <- "/home/garofalo/analysis/blinded_gm2/data/out/"
df <- NULL
for (i in seq_along(e)) {

mt <- read_df(paste0(dir, e[i], "_output"))
all_obs <- Rose::get_all_corr(mt)
name<-"amu_{bound}_(TM)_above"
df <- add_corr_to_df(string =name, all_obs, mt, df,
  reshape = FALSE, nudge = 0.0+(i-1)*0.2,print_res = FALSE, rename = paste0(name,confs[i]), ifit=5, idfit=6
)
name<-"amu_{bound}_(TM)_below"
df <- add_corr_to_df(name, all_obs, mt, df,
  reshape = FALSE, nudge = 0.1+(i-1)*0.2, rename = paste0(name,confs[i]), ifit=5, idfit=6
)
name<-"amu_{bound_meff_t}_(TM)_below"
df <- add_corr_to_df(name, all_obs, mt, df,
  reshape = FALSE, nudge = 0.05+(i-1)*0.2, rename = paste0(name,confs[i]), ifit=5, idfit=6
)
name<-"amu_{bound_meff}_(TM)_above"
df <- add_corr_to_df(name, all_obs, mt, df,
  reshape = FALSE, nudge = 0.15+(i-1)*0.2, rename = paste0(name,confs[i]), ifit=5, idfit=6
)
}
###############################################################################


gg <- plot_df_corr_ggplot(df)


fig <- myplotly(gg, to_print = TRUE)
```


```{r, results='asis',echo=FALSE}
e <- c("D96_444confs", "D96_256confs", "D96_184confs", "D96_122confs")
confs <- c(444, 256, 184, 122)
df <- NULL
dir <- "/home/garofalo/analysis/blinded_gm2/data/out/"

for (i in seq_along(e)) {
  mt <- read_df(paste0(dir, e[i], "_output"))
  all_obs <- Rose::get_all_corr(mt)

  fit <- get_full_res("amu_{bound}_(TM)_ave", all_obs, mt)
  fit_meff_t <- get_full_res("amu_{bound_meff_t}_(TM)_ave", all_obs, mt)
  fit_meff <- get_full_res("amu_{bound_meff}_(TM)_ave", all_obs, mt)
  fit_OS <- get_full_res("amu_{bound}_(OS)_ave", all_obs, mt)
  fit_OS_meff_t <- get_full_res("amu_{bound_meff_t}_(OS)_ave", all_obs, mt)
  fit_OS_meff <- get_full_res("amu_{bound_meff}_(OS)_ave", all_obs, mt)

  dft <- data.frame(
    "Nconf" = confs[i],
    "amu_{bound}_(TM)" = fit[1, 1],
    "damu_{bound}_(TM)" = fit[1, 2],
    "amu_{bound_meff_t}_(TM)" = fit_meff_t[1, 1],
    "damu_{bound_meff_t}_(TM)" = fit_meff_t[1, 2],
    "amu_{bound_meff}_(TM)" = fit_meff[1, 1],
    "damu_{bound_meff}_(TM)" = fit_meff[1, 2],
    "amu_{bound}_(OS)" = fit_OS[1, 1],
    "damu_{bound}_(OS)" = fit_OS[1, 2],
    "amu_{bound_meff_t}_(OS)" = fit_OS_meff_t[1, 1],
    "damu_{bound_meff_t}_(OS)" = fit_OS_meff_t[1, 2],
    "amu_{bound_meff}_(OS)" = fit_OS_meff[1, 1],
    "damu_{bound_meff}_(OS)" = fit_OS_meff[1, 2]
  )
  df <- rbind(df, dft)
}
gg <- myggplot()

############################################################################
lab<-"damu_{bound_meff_t}_(TM)"
gg <- gg + geom_point(aes(
  x = 1 / sqrt(df$Nconf),
  y = df$damu_.bound_meff_t._.TM.,
  color = !!lab
))

df$x <- 1 / sqrt(df$Nconf)
lm_fit <- lm(damu_.bound_meff_t._.TM. ~ 0 + x, data = df)
tmp<-data.frame(x=c(df$x,0))
predicted_df <- data.frame(mpg_pred = predict(lm_fit, tmp), x = tmp$x)
gg <- gg + geom_line(aes(x = tmp$x, y = !!predicted_df$mpg_pred,color = !!lab))
#########################################################################
lab<-"damu_{bound_meff_t}_(OS)"
gg <- gg + geom_point(aes(
  x = 1 / sqrt(df$Nconf),
  y = df$damu_.bound_meff_t._.OS.,
  color = !!lab
))

tmp<-data.frame(x=c(df$x,0))
lm_fit <- lm(damu_.bound_meff_t._.OS. ~ 0 + x, data = df)
predicted_df <- data.frame(mpg_pred = predict(lm_fit, tmp), x = tmp$x)
gg <- gg + geom_line(aes(x = tmp$x, y = !!predicted_df$mpg_pred, color = !!lab))
#######################################################à
lab<-"amu_{bound_meff}_(TM)"
gg <- gg + geom_point(aes(
  x = 1 / sqrt(df$Nconf),
  y = df$damu_.bound_meff._.TM.,
  color = !!lab
))

df$x <- 1 / sqrt(df$Nconf)
lm_fit <- lm(damu_.bound_meff._.TM. ~ 0 + x, data = df)
tmp<-data.frame(x=c(df$x,0))
predicted_df <- data.frame(mpg_pred = predict(lm_fit, tmp), x = tmp$x)
gg <- gg + geom_line(aes(x = tmp$x, y = !!predicted_df$mpg_pred,color = !!lab))
#########################################################################
lab<-"amu_{bound_meff}_(OS)"
gg <- gg + geom_point(aes(
  x = 1 / sqrt(df$Nconf),
  y = df$damu_.bound_meff._.OS.,
  color = !!lab
))

tmp<-data.frame(x=c(df$x,0))
lm_fit <- lm(damu_.bound_meff._.OS. ~ 0 + x, data = df)
predicted_df <- data.frame(mpg_pred = predict(lm_fit, tmp), x = tmp$x)
gg <- gg + geom_line(aes(x = tmp$x, y = !!predicted_df$mpg_pred, color = !!lab))



#
fig <- myplotly(gg, "", "$1/\\sqrt{N}$", to_print = TRUE, xrange=c(0,0.093), yrange=c(0,1.05e-9))
```
